High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-10-16 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

Ring13 is surprisingly narrow and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig. \ref{fig:two}). We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.1\pm0.04$\,mas, relative to the stars.

@@

Repeating the optimization of the disk orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars. We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star. Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig. \ref{fig:polarring}, perhaps due to the joint effect of all these small differences. ***CALCULATE THE CHI2 DIFFERENCE BETWEEN THE TWO TRACES? SOME FORM OF STATS WOULD BE GOOD***

@@

The simulated 1.3\,mm continuum image displays some clear similarities with the ALMA observation. The model reproduced the two rings that are present in the observation: the faint inner Ring13 and the outer brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig. \ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner Ring13. Accordingly, taking the parametric model values for the large-dust Ring13 we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$. For Ring24, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$.

@@

  \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au. The location of this ring is similar to the inner ring observed in the scattered-light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.

@@

%\item The inner ring may not be totally resolved as its width is comparable to the beam size. Future observation with smaller beams sizes could give an answer on the real radial extent of the ring.

>>>>

Ring13 is surprisingly narrow and seems to be off-centre relative to the GAIA stellar position (at the origin of coordinates in Fig. \ref{fig:two}). We determined the ring's centre and orientation by minimising the dispersion of the disc radial profiles, from 6\,au to 19\,au, and thus obtained a PA of 74.64$\pm$0.08\,$\degr$, an inclination of 33.90$\pm$0.04\,$\degr$ and a centre at $\Delta \alpha = 9\pm0.05$\,mas $\Delta \delta = 0.06\pm0.04$\,mas, relative to the stars.

@@

Repeating the optimization of the disk orientation, but this time aiming for Ring24 with a radial domain from 20\,au to 70\,au, we obtained a PA of 76.78$\pm$0.03\,$\degr$, with an inclination of 34.01$\pm$0.01\,$\degr$ and a centre at $\Delta \alpha = 19\pm0.04$\,mas $\Delta \delta = 7\pm0.03$\,mas relative to the stars. We see that both Ring13 and Ring24 both share the same orientation and centre, given the errors, and both are offset from the star. Even though all orientation parameters for Ring13 and Ring24 are consistent within the errors, there are however some hints for a different orientation, as summarised in Fig. \ref{fig:polarring}, perhaps due to the joint effect of all these small differences.***

@@

The simulated 1.3\,mm continuum image displays some clear similarities with the ALMA observation. The model reproduced the two visible rings: the faint inner Ring13 and the outer brighter Ring24. As the radial profiles obtained from the simulated images of the model closely resemble those deduced from the observations (Fig. \ref{fig:radprofiles}), we can assume that the model provides a reliable approximation of the disc structure, including, particularly for our interest, the dimensions of the previously unseen 1.3\,mm thin inner Ring13. Accordingly, taking the parametric model values for Ring13 we have that it is located at 13.6\,au, has an estimated width of 2.6\,au, an estimated scale height ranging from 0.25 to 0.32\,au and a dust mass of about 3\,M$_{\earth}$. For Ring24, we have that it has an intensity peak at $\sim$30\,au, a break present at $\sim$35\,au and a mass of $\sim$43\,M$_{\earth}$.

@@

  \item We report a narrow inner ring for the 1.3\,mm continuum located at 13.46$\pm$0.43\,au from the stars and has an estimated width of 4.17$\pm$0.94\,au. The location of this ring is coincident with the inner ring observed in the scattered-light image, revealing that the ring includes a considerable mass of millimetre-sized grains of around 3\,M$_{\earth}$. Using the parametric model scale height value ($h= $ 0.28\,au at 13.46\,au) we have that the ring width is $\sim$15 times its estimated height, making it a stable ring.

@@
